Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2018-12-10 tex/WW4C_VHzQ.tex
Another decent update for SEDs, Nofz directory

At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ iobserved, 
i.e., in the $z$-band, while at

>>>>

The Pan-STARSS1 $z_{\rm PS1}$ and $y_{\rm PS1}$-bands approximatley
sample the redshift ranges $4.53\leq z \leq 5.45$ and $5.28\leq z \leq 6.47$, respectively 
for 1450\AA'\ emission, while the VIRCAM $Y_{\rm VIRCAM}-$ and $J_{\rm VIRCAM}$-bands 
cover $5.50\leq z \leq 6.57$ and $7.06\leq z \leq 8.16$.

%At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ observed, i.e., in the $z$-band, while at $z=6.00$, $z=5.00$
